Code used to generate paper results : Database comparison and CT characteristics

### 2024-05-29 Paper_code-CT_analysis.Rmd
Changed spermatid to post meiotic cells

```{r, eval = TRUE, echo=FALSE}
pdf(file = paste0("figs/GTEX_Tumors.pdf"))
draw(h_list, main_heatmap = "TCGA (logTPM)", 
     ht_gap = unit(c(0.3, 0.01), "cm"),
     merge_legend = TRUE)
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Multimapping.pdf"))
draw(h_list, main_heatmap = "log(TPM)", ht_gap = unit(0.3, "cm"),
                 height = unit(5, "cm"))
dev.off()
```

@@

```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Methylation_classification.pdf"))
draw(h_list, main_heatmap = "Mean \nmethylation", ht_gap = unit(0.5, "cm"), 
     merge_legend = TRUE)
dev.off()
```

@@

```{r, eval = TRUE, echo=FALSE}
pdf(file = paste0("figs/X_enrichment.pdf"), width = 7, height = 4)
cowplot::plot_grid(met_prop_fig, fig_X_enrichment, labels = c('A', 'B'), 
          rel_widths = c(1, 2),
          label_size = 12)
dev.off()
```

@@

```{r}
pdf(file = paste0("figs/Methylation_panel.pdf"), width = 7, height = 4)
cowplot::plot_grid(left_fig, right_fig, 
          rel_widths = c(2,1),
          scale = c(1, 0.8),
          label_size = 10, nrow = 1,
          align = "h")
dev.off()
```

@@

fig_mean_prop_in_tum
```
```{r, eval = TRUE, echo = FALSE}
pdf(file = paste0("figs/Mean_prop_in_tumors.pdf"), width = 5, height = 4)
fig_mean_prop_in_tum
dev.off()
```

@@

```{r, echo = FALSE, eval = TRUE}
pdf(file = "figs/CT_met_AUC_hypo_TCGA.pdf", height = 2.3, width = 3)
draw(h1, column_title = "CT genes regulated by methylation",
     column_title_gp = gpar(fontsize = 5), show_heatmap_legend = TRUE,
     show_annotation_legend = TRUE, heatmap_legend_side = "bottom",
     merge_legend = TRUE)
dev.off()

@@

```{r, echo = FALSE}
pdf(file = paste0("figs/CT_met_AUCscore_hypo_TCGA.pdf"), height = 2.5)
f1
dev.off()

@@

# add meiotic stage to the colData of testis_sce
testis_sce$stage <- "pre-meiotic"
testis_sce[, testis_sce$type %in% 
             c("Early_spermatocyte", "Late_spermatocyte", 
               "Round_spermatid")]$stage <- "meiotic"
testis_sce[, testis_sce$type %in% 
             c("Elongated_spermatid", "Sperm")]$stage <- "post-meiotic"
testis_sce[, testis_sce$type %in% 
             c("Macrophage", "Endothelial", "Myoid", "Sertoli", 
               "Leydig")]$stage <- "somatic"
testis_sce$stage <- factor(
  testis_sce$stage, 
  levels = c("pre-meiotic", "meiotic", "post-meiotic", "somatic"))

@@

```{r, echo = FALSE, eval = TRUE}
pdf(file = paste0("figs/CT_in_GermCells.pdf"), width = 6, height = 4)
draw(ht_list, main_heatmap = "Logcounts", 
     merge_legend = TRUE, 
     ht_gap = unit(0.2, "cm"), 
     legend_gap = unit(0.15, "cm"),
     legend_grid_height = unit(0.08, "cm"),
    legend_grid_width = unit(0.1, "cm"))
dev.off()
```

>>>>

```{r, eval = FALSE, echo=FALSE}
pdf(file = paste0("figs/GTEX_Tumors.pdf"))
draw(h_list, main_heatmap = "TCGA (logTPM)", 
     ht_gap = unit(c(0.3, 0.01), "cm"),
     merge_legend = TRUE)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Multimapping.pdf"))
draw(h_list, main_heatmap = "log(TPM)", ht_gap = unit(0.3, "cm"),
                 height = unit(5, "cm"))
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Methylation_classification.pdf"))
draw(h_list, main_heatmap = "Mean \nmethylation", ht_gap = unit(0.5, "cm"), 
     merge_legend = TRUE)
dev.off()
```

@@

```{r, eval = FALSE, echo=FALSE}
pdf(file = paste0("figs/X_enrichment.pdf"), width = 7, height = 4)
cowplot::plot_grid(met_prop_fig, fig_X_enrichment, labels = c('A', 'B'), 
          rel_widths = c(1, 2),
          label_size = 12)
dev.off()
```

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Methylation_panel.pdf"), width = 7, height = 4)
cowplot::plot_grid(left_fig, right_fig, 
          rel_widths = c(2,1),
          scale = c(1, 0.8),
          label_size = 10, nrow = 1,
          align = "h")
dev.off()
```

@@

fig_mean_prop_in_tum
```
```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/Mean_prop_in_tumors.pdf"), width = 5, height = 4)
fig_mean_prop_in_tum
dev.off()
```

@@

```{r, echo = FALSE, eval = FALSE}
pdf(file = "figs/CT_met_AUC_hypo_TCGA.pdf", height = 2.3, width = 3)
draw(h1, column_title = "CT genes regulated by methylation",
     column_title_gp = gpar(fontsize = 5), show_heatmap_legend = TRUE,
     show_annotation_legend = TRUE, heatmap_legend_side = "bottom",
     merge_legend = TRUE)
dev.off()

@@

```{r, eval = FALSE, echo = FALSE}
pdf(file = paste0("figs/CT_met_AUCscore_hypo_TCGA.pdf"), height = 2.5)
f1
dev.off()

@@

# add meiotic stage to the colData of testis_sce
testis_sce$stage <- "pre-meiotic"
testis_sce[, testis_sce$type %in% 
             c("Early_spermatocyte", "Late_spermatocyte")]$stage <- "meiotic"
testis_sce[, testis_sce$type %in% 
             c("Round_spermatid","Elongated_spermatid", 
               "Sperm")]$stage <- "post-meiotic"
testis_sce[, testis_sce$type %in% 
             c("Macrophage", "Endothelial", "Myoid", "Sertoli", 
               "Leydig")]$stage <- "somatic"
testis_sce$stage <- factor(
  testis_sce$stage, 
  levels = c("pre-meiotic", "meiotic", "post-meiotic", "somatic"))

@@

```{r, echo = FALSE, eval = FALSE}
pdf(file = paste0("figs/CT_in_GermCells.pdf"), width = 6, height = 4)
draw(ht_list, main_heatmap = "Logcounts", 
     merge_legend = TRUE, 
     ht_gap = unit(0.2, "cm"), 
     legend_gap = unit(0.15, "cm"),
     legend_grid_height = unit(0.08, "cm"),
    legend_grid_width = unit(0.1, "cm"))
dev.off()
```
